---
title: "DMA Theme Data-Visualization Palettes"
author: "Dunsworth-Mann Analytics LLC"
output:
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 8, fig.height = 4)
# Adjust path if knitting from elsewhere
source("dma_palette.R")
source("ggplot2_dma.R")
has_ggplot2 <- requireNamespace("ggplot2", quietly = TRUE)
```

# DMA Theme Data-Visualization Palettes

Brewer-style schemes built from DMA brand colors: qualitative,
sequential, and diverging.

## Qualitative (categorical)

```{r}
dma_qualitative_colors
```

## Sequential ramps

Light to dark, `n` colors on demand:

```{r}
dma_sequential("Teals", 7)
dma_sequential("Cool", 5)     # multi-hue: green -> teal -> blue
```

## Diverging

End -> pale neutral center -> other end. Odd `n` places the neutral
exactly at the midpoint:

```{r}
dma_diverging("Red-Blue", 7)
```

## Semantic status colors

All meet WCAG AA (>= 4.5:1) on white:

```{r}
dma_status_colors()
```

## ggplot2 examples

```{r, eval=has_ggplot2}
library(ggplot2)
df <- data.frame(
  x = rep(1:9, each = 3),
  grp = factor(rep(LETTERS[1:3], 9)),
  z = seq(-1, 1, length.out = 27)
)
```

### Categorical

```{r categorical, eval=has_ggplot2, fig.height=3}
ggplot(df, aes(x, fill = grp)) +
  geom_histogram(binwidth = 1, position = "dodge", color = NA) +
  scale_fill_dma() +
  labs(title = "scale_fill_dma()", x = NULL, y = NULL) +
  theme_minimal(base_size = 11)
```

### Continuous sequential

```{r sequential, eval=has_ggplot2, fig.height=3}
ggplot(df, aes(x, grp, fill = z)) +
  geom_tile(color = "white") +
  scale_fill_dma_continuous("Cool") +
  labs(title = 'scale_fill_dma_continuous("Cool")', x = NULL, y = NULL) +
  theme_minimal(base_size = 11)
```

### Diverging

```{r diverging, eval=has_ggplot2, fig.height=3}
ggplot(df, aes(x, grp, fill = z)) +
  geom_tile(color = "white") +
  scale_fill_dma_diverging("Red-Green") +
  labs(title = 'scale_fill_dma_diverging("Red-Green")', x = NULL, y = NULL) +
  theme_minimal(base_size = 11)
```

## Plotly

```{r, eval=requireNamespace("plotly", quietly = TRUE)}
source("plotly_dma.R")
dma_colorscale("Ocean")   # pass to plot_ly(..., colorscale = ...)
```
